Paper_Figure

### 2025-04-23 README.Rmd
250422

``` r
install.packages("devtools")
devtools::install_github("ruiqi0130/LocalizedMarkerDetector")

@@

## Example tutorial
Please check [LMD tutorial](https://ruiqi0130.github.io/LocalizedMarkerDetector/articles/).

## References
References of LMD functions can be found [here](https://ruiqi0130.github.io/LocalizedMarkerDetector/reference/index.html).

>>>>

``` r
install.packages("devtools")
devtools::install_github("KlugerLab/LocalizedMarkerDetector")

@@

## Example tutorial
Please check [LMD tutorial](https://KlugerLab.github.io/LocalizedMarkerDetector/articles/).

## References
References of LMD functions can be found [here](https://KlugerLab.github.io/LocalizedMarkerDetector/reference/index.html).
